---
title: "Map of Typhi Cases and River Positivity"
author: "Chris LeBoa"
date: "2020/02/05"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Load Libraries

You can include R code in the document as follows:

```{r cars}


library(tidyverse)
library(sf)
library(leaflet)


```

## Parameters

```{r}
#Parameters 

myLocation <- c(85.2, 27.6, 85.61, 27.7)

file_location_cases <- here::here("data/cases/all_cases.shp")
file_location_rivers <- here::here("data/rivers/rivers.shp")
file_location_water_samples <- here::here("data/water_samples/water_samples.shp")

#install.packages("rnaturalearth")
#install.packages("rnaturalearthdata")

library("rnaturalearth")
library("rnaturalearthdata")

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

#Read in Data
```{r}
cases <- read_sf(file_location_cases)
rivers <- read_sf(file_location_rivers)
water_positivity <- read_sf(file_location_water_samples)




```
#Map Data
```{r}
myMap <- 
  get_map(
  location = myLocation,
  #maptype = "satellite",
  #source = "osm",
  crop = FALSE
  )
#source="stamen",
#maptype=“watercolor",
ggmap(myMap) +
  ggplot() +
  geom_polygon(data = read_sf aes(x = long, y = lat))

ggmap(myMap) + 
  geom_sf(data = cases$geometry)


country_nepal <- 
  ne_countries(country = "nepal")


cases %>% 
  ggplot(x = ) +
  geom_sf()

```


#Wondering why get_map isnt working like it should 
```{r}
(map <- get_map(c(left = -97.1268, bottom = 31.536245, right = -97.099334, top = 31.559652)))
ggmap(map)


# characters default to google
(map <- get_map("orlando, florida"))
ggmap(map)

#Google map ex
poland <- get_googlemap(c(lon=19.27, lat=52.03),
                     zoom = 6, 
                     maptype = "satellite")
```

# Maps using Leaflet

```{r}

#install.packages("leaflet")

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(data = cases, color = "red")
  
  #adjust size and alpha of the circle markers 
  #try mapbox static options 
  
  #addCircleMarkers(data = water_positivity + proj(longlat)) %>% 
  addPolygons(
    data = rivers,
    color = "blue",
    weight = 2
  )
```

